A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-16 manuscript/reply_to_reviewers.tex

\begin{document}

\newpage

\setcounter{page}{1}

% Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly. Changed filtering to reflect all uncertainty, not just detection (more accurate, hopefully less confusing). No box needed, just ``Why sample'' section.

@@

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address them.

	Reviewer 2 takes a different view of the purpose and scope of the manuscript from that of the other reviewers. We respect his/her ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasise that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. Please note that Reviewer 3 identified this need explicitly. 
	% Tomas has a line break here, I'm not sure.
	Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. However, we hope and trust that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.

	As a key point of departure for our revision, we have taken Reviewer 1's suggestion that we expand upon the different types of priors available and reasons for choosing one over the other. We also now offer a brief discussion about concerns over the subjectivity of prior selection. We argue that a great deal of subjectivity is baked into the compilation of empirical networks and that a Bayesian approach can be seen as making this subjectivity explicit. We hope that this will encourage empiricists to explicitly use their system-specific knowledge to create reasonable priors, as likely already occurs subconsciously (as in the designation of ``forbidden links``).

	Overall, we hope that our revision more clearly frames the importance of uncertainty in ecological networks and positions a simple Bayesian approach as a partial solution (together with high-quality sampling, of course). 
	We have also added many references to prior work. While the present study is not intended to be a full review of the literature, we certainly do not wish to downplay other workers in the area.
	Finally, several of the Reviewers appeared to believe that we were advocating for reduced sampling effort. That is emphatically not the case (we had not anticipated that anyone would seriously consider sampling less than they otherwise would when using our framework), and we have revised the manuscript to be clearer about the fact that increased sampling effort can reduce some sources of uncertainty and that high-quality sampling should form the basis of any empirical network. We hope that it is now clear that the Bayesian framework we promote is a complement to excellent field work, not a replacement for it.

@@

	Once again, we thank the Associate Editor and Reviewers for their comments and hope that our revised manuscript will satisfy their concerns.

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	The Reviewer complimented our manuscript as ``well-written'' and addressing the ``hugely important'' question prior choice in network analyses. He/she supports our suggestion that researchers use their system-specific knowledge when embarking upon Bayesian analyses, and has suggested that we restructure the manuscript (especially the introduction) in order to come more directly to the issue of prior choice. In the present revision we have taken this advice to heart and streamlined our introduction in order to expand our discussion of prior choice. In this revision, we have retained some of the introductory material, which the Reviewer notes describes ``ground very well-trod'', in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand. We hope that the introduction now strikes a balance between providing essential background information for Bayesian novices and moving quickly enough for those who do not need such a gentle introduction. We thank the Reviewer for their feedback and address each point (prefaced by \textbf{R:}) below.

@@

	1. Suggestion to refocus on prior selection

		\begin{refquote}
			In ecology more broadly, priors are treated with timidity, as if we couldn't dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. ... Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be at least touched on in the discussion. 
			\end{refquote}

		\textbf{R:} We thank the Reviewer for his/her positive evaluation, and have done our utmost to reframe and tighten the introduction and framing of the paper. In doing so, we have happily adopted the suggestion to expand our discussion of prior selection, particularly with regard to approximate/empirical Bayes. Although we are somewhat space-limited, we have expanded our description of the different priors available and why a researcher might choose one over another (section beginning with line 200). We also touch upon the controversy over using empirical priors (lines 283-289) although we were unable to find many references addressing this in detail. We hope that this expanded description will be a better guide for empiricists who may not be familiar with Bayesian statistics.

		In implementing the Reviewer's comments on our introduction, we believe that most readers who are less familiar with Bayesian procedures will need a quick outline of the problem of uncertain detection of interactions in order to be motivated to dive into the larger discussion of priors. We stress that our intended target audience is empirical ecologists working on network description who likely have a different skillset than that of the Reviewer. We also note that Reviewer 2 found that \emph{``The introduction is particularly pleasant to read and the problem is well stated``}, praise which we would hate to lose. Therefore we have revised and streamlined our introduction but still refrain from jumping straight into prior selection. We have, however, taken care to introduce our analysis as a worked example (lines 200-201) and hope that this helps to reduce the conflict between the introduction and our data.

@@

		\begin{refquote}
		The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations. We have incorporated these references as suggested (including Jordano, 2016 in the sampling section). Following comments from other reviewers, we have refined and restructured our introduction in the hope of more clearly establishing the goal of our manuscript. We hope that this revised introduction will also meet with the Reviewer's approval.

	3. Suggestion to de-emphasise MLE estimate and get straight to Bayes

		\begin{refquote}
		It's a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use. Moreover, it helps to formalise our argument that most networks are undersampled, justifying the Bayesian approach and the use of priors to reduce/set bounds around the resulting uncertainty. We therefore feel that it is important to keep some discussion of the MLE estimate in the manuscript. We now introduce the MLE formally within this context (lines 179-184) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure S2, \emph{Appendix S2}}).

		Lines 179-184:

		\begin{quotation}
			The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrences $n_{ij}$: $\lambda_{ij}=\frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for $\lambda_{ij}$ is the beta distribution:
		\end{quotation}

		Caption of Figure S2:

@@

		\begin{quotation}
			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig. 3), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
		\end{quotation}

	4. Suggestion to remove moments of the beta distribution

		\begin{refquote}
		I think a bit of space is wasted on defining the moments of the beta distribution. This is very googleable, and almost too thorough. I think the space is better utilised aligning the ecological challenge and the quantitative method.
		\end{refquote}

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S3. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

@@

	5. Novelty of the study not clear in current framing

		\begin{refquote}
		I'm wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn't been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasise the board applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). Finally, we note that there is a need to synthesise the literature on sampling issues and formalise the sources of uncertainty affecting the estimation of pairwise interactions. There are, as the Reviewer notes, already a number of publications addressing probabilistic interactions, but none of them adequately characterise uncertainty about interactions. We hope that the contribution our manuscript makes is now clearer.

@@

	6. Potential contradiction

		\begin{refquote}
		L89 for example, seems to conflict with the two paragraphs immediately following it?
		\end{refquote}

		\textbf{R:} We now address questions of sampling in the paragraph beginning with line 168 and in Appendix S2. We hope that this revision makes it clear that sampling should be as high-quality as possible but that sampling is unlikely to completely remove uncertainty.

	% 	Literature suggestions:
		% Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
		% Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
		% Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
		% Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
		% Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
		% Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
		% Wells, K., & O'Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

@@

\clearpage

% ----------------------------------------------------------------------
% ---------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#2} 
% ---------------------------------------

	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainty of interactions'' which he/she rates as ``one of the hottest topics in the field``. He/she also points out that ``the introduction is particularly pleasant to read'' and that we framed the problem well. The Reviewer also pointed out a number of weaknesses to the manuscript that we respond to one-by-one. In general, we feel that the Reviewer's comments reflect a high degree of statistical expertise; expertise that we do not expect to be shared by the bulk of our intended audience (empirical ecologists assembling new ecological networks). We have therefore prioritised comments by this and the other Reviewers that seemed most likely to improve the manuscript for readers who are relatively new to Bayesian analysis over concerns most relevant to a highly knowledgeable reader. We hope that our revised manuscript makes this target audience clearer, and that we have addressed the Reviewer's key concerns with our revision. Below, we respond to each of the Reviewer's comments (preceded by \textbf{R:}) in turn.

	1. Lack of references

@@

		\begin{refquote}

			The fundamental question about predicting interactions given some uncertainty has been and is debated in many papers (see the seminal paper by Roger Guimer\`{a} and Marta Sales-Pardo, PNAS, 2009). Even if the proposed framework is probably not stated in its exact terms in the literature, bridges between existing approaches (beyond Ecology) and the one in the paper would be very welcomed. An appropriate discussion between points of convergence and difference would help the reader to appreciate the significance and the impact of the proposed methodology.

		\end{refquote}

		\textbf{R:} This comment echoes the impression of Reviewers 1 (above) and 3 (below) that we do not give adequate attention to previous work. As stated above, we have now added many further pointers to previous work, and also been much more explicit regarding whom we try to reach with what message in the current paper. We have also included references from medical and epidemiological research as examples of the use of Bayesian methods beyond ecology.

	2. Non-independence of interactions not accounted for

		\begin{refquote}
			2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data. Indeed, the paper is supposed to be ``network-oriented'' but the methodology deals with independent interactions (e.g. the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole). Consequently, the mathematical framework remains quite simple and may not reflect nor model the processes governing the actual detection of interactions. Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,
		\end{refquote}

		\textbf{R:} We agree wholeheartedly that ecological interactions are often not independent. Indeed, some of the priors we discuss (e.g., those incorporating species' abundances or trait-matching) will introduce covariance between interactions. The Reviewer is correct that we did not initially mention this non-independence explicitly. Our aim is to keep our mathematical framework simple so that it is easy for those not familiar with Bayesian analysis to adopt. Nevertheless, non-independence of interactions is an important consideration. We are therefore happy to index all variables referring to interactions by ij and we have added explicit statements (lines 186-190 and 248-255) that some priors treat interactions independently while others will introduce covariance (e.g., by species).

		Lines 186-190:

@@

		\begin{quotation}
		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
		\end{quotation}

		Lines 248-255:

		\begin{quotation}
			Multiple sources of information can be combined into a single model (e.g., the the $K$ nearest neighbour (KNN) algorithm, which identifies likely interaction partners based on similarity to known partners~\citep{DesjardinsProulx}). This would result in a highly informative prior that would, moreover, account for some of the non-independence in interaction probabilities.

	        Using an informative prior like these tailors the level of uncertainty surrounding each interaction and may account for non-independence of interactions (as in abundance-based or KNN models).
	    \end{quotation}

	3. Question about identifiability of the model

@@

		\begin{refquote}

			the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainty are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

		\end{refquote}

		\textbf{R:} We believe that this comment stems from a lack of clarity about the goal of our model. It is not designed to separate the three levels of uncertainty or introduce parameters at particular levels. The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences. Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines 159-167 and lines 199-201). We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one. Instead, we refer interested readers to~\citet{Weinstein2017} which does attempt to separate sources of uncertainty.

		Lines 159-167:

		\begin{quotation}
			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij}=0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij})=k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
		\end{quotation}

		Lines 199-201:

		\begin{quotation}
			 Note that these models of $\lambda_{ij}$ do not distinguish between sources of uncertainty except through the choice of prior. For a model which attempts to separate sources of uncertainty, see~\citet{Weinstein2017}.
		\end{quotation}

	4. Request for a simulation study

		\begin{refquote}
			the authors proposed an original approach based on a Bayesian framework. Beyond the identifiability question (see above), the reader can question the power of the method. Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it. In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset... In my opinion, the reader can't be fairly convinced: how powerful is the method? what can we say about the priors? how much data (n, k) is necessary to expect good results? An so on... Only a well-conducted simulation study can answer these questions.
		\end{refquote}

### 2019-01-16 manuscript/CI_interactions.tex
added Dom comments to reply

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6871 % Limit is 6000-7000 including figs, tables, references. 
% \end{itemize}
% \end{minipage}
% }

@@

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using perhaps the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions. This uncertainty can, however, be constrained with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. By using a comprehensively sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions. 
    \item Overall, we demonstrate the utility of our approach, given the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE.
\end{enumerate}

@@

\linenumbers
\clearpage

@@

    Representing an ecological community as a network allows ecologists to address both community composition and the interactions between species~\citep{Roslin2016}. Identifying these interactions is critical to understanding species' effects on each other and predicting the community's response to perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of links between species. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework for combining observed data with a prior expectation of network structure. This prior expectation can be uninformative, or it may include prior knowledge about the study system. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

    \subsection*{Why do some interactions \emph{not} occur?}

      We start from the perspective of a community ecologist wishing to describe an interaction network. This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}. While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not the interaction truly occurred} (Fig.~\ref{conceptual_fig}). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait-matching between species $i$ and $j$ $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}, leaving some uncertainty about whether some species pairs could interact.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

>>>>

% \begin{minipage}[h]{0.6\textwidth}
% \begin{itemize}
% \item Running title: Quantitative network construction
% \item Number of references: 37
% \item Number of figs, tables, \& text boxes: 4 % Limit is 10
% \end{itemize}
% \end{minipage}\begin{minipage}[h]{0.4\textwidth}
% \begin{itemize}
% \item Abstract word count: 290
% \item Main text word count: 6973 % Limit is 6000-7000 including figs, tables, references. Would be good to include Dom2018 if I can trim a bit more.
% \end{itemize}
% \end{minipage}
% }

@@

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using perhaps the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions. This uncertainty can, however, be constrained with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance and nestedness. Even with informative priors, we are likely to miss many interactions that may occur rarely or under different local conditions. 
    \item Overall, we demonstrate the importance of acknowledging the uncertainty inherent in network studies, and the utility of treating interactions as probabilities in pinpointing areas where more study is needed. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE.
\end{enumerate}

@@

% \linenumbers
\clearpage

@@

    Representing an ecological community as a network addresses both community composition and interspecific interactions~\citep{Roslin2016}. Identifying these interactions is critical to understanding species' effects on each other and predicting community responses to perturbations~\citep{Bartomeus2016,Giron2018}. Importantly, information is conveyed both by the presence and \emph{absence} of interactions. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed~\citep{Jordano2016}.

    First, ecological communities are stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilities and hence interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers note effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Jordano2016}). Assessments of the accumulation of interactions with increasing sampling effort suggest that it is more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeus2013,Poisot2016}. Such efforts usually take the form of creating model networks that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Model networks provide an important ''reality check'' by allowing hypothesis testing about factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}. They can also allow estimation of the numbers unobserved of interactions~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case such a model may be a poor fit for a particular study system. Moreover, some of the models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2006} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes rarely-observed species.

    Here we introduce a simple, adaptable Bayesian framework. First, we briefly describe the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling~\citep{Bartomeus2013}), we present a Bayesian framework which combines observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled host-parasitoid network. We find that even the highest-quality empirical network data we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. 
    % We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

    \subsection*{Why are some interactions not observed?}

      We start from the perspective of a community ecologist describing an interaction network. This ecologist will be interested in describing the species/nodes present and the links between them~\citep{Roslin2016}. While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"

@@

          Fundamentally, some interactions are feasible while others are not~\citep{Poisot2015}. An unobserved interaction may have $\lambda_{ij}>0$, and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some function describing trait matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}})=\lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. In some cases the traits prohibiting an interaction are known and there will be little uncertainty about $\lambda_{ij}$. Generally, however, the traits that might prohibit an interaction are unknown~\citep{Dormann2017} and uncertainty about $\lambda_{ij}$ will be high. 
          %Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.
          As trait-matching models improve, uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. This leaves some uncertainty about whether some species pairs could interact.

@@

            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden" by spatio-temporal mismatch could potentially occur.
